---
title: "benchmark"
author: "Chelsea Matthews"
date: "13 May 2020"
output: 
  html_document:
      code_folding: "show"
      number_sections: TRUE
      toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
											results = "asis",
											message = FALSE, warning = FALSE,
											error = FALSE)
```

```{r}
library(plyr)
library(tidyverse)
library(ggplot2)
library(grImport)
library(XML)
library(kableExtra)
library(cluster)
library(purrr)
library(data.table)
library(ggpubr)
library(scales)
library(viridis)
library(dplyr)
library(cowplot) 
library(egg) 
library(ggnewscale)
library(readr)
library(lubridate)
library(magrittr)
```

# Reading in benchmarking data

```{r}
clr_benchmark_files <- dir("../pacbio_clr/benchmarks", recursive=TRUE, full.names=TRUE, pattern=".tsv$")

clr_bench <- as_tibble(plyr::ldply(clr_benchmark_files, read.delim))

newCols <- c("rule_name",
             "threads",
             "read_type", 
             "assembly_type", 
             "assembly_tool", 
             "read_selection", 
             "prefix", 
             "bbduk_cov", 
             "bbduk_kmer", 
             "depth",
             "polishdepth",
             "polishselect",
             "polishround")

clr_bench[,newCols] <- NA

for( i in 1:length(clr_benchmark_files)) {
  temp <- unlist(strsplit(clr_benchmark_files[i], "/"))
  temp <- unlist(strsplit(temp, "_"))
  temp <- unlist(strsplit(temp, "\\."))
  clr_bench[i,"rule_name"] <- temp[match("benchmarks", temp) +1]
  clr_bench[i,"read_type"] <- "clr"
  clr_bench[i,"assembly_type"] <- temp[match("assemblytype", temp) +1]
  clr_bench[i,"assembly_tool"] <- temp[match("assemblytool", temp) +1]
  clr_bench[i,"read_selection"] <- temp[match("readselect", temp) +1]
  clr_bench[i,"prefix"] <- temp[match("prefix", temp) +1]
  clr_bench[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  clr_bench[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  clr_bench[i,"depth"] <- temp[match("depth", temp) +1]
  clr_bench[i,"polishdepth"] <- temp[match("polishdepth", temp) +1]
  clr_bench[i,"polishround"] <- temp[match("polishround", temp) +1]
  clr_bench[i,"polishselect"] <- temp[match("polishselect", temp) +1]
}

clr_bench$depth <- as.numeric(clr_bench$depth)

#change rule_name flyegenome to flye.
clr_bench$rule_name <- str_replace(clr_bench$rule_name, "flyegenome", "flye")

#====================================================================
#HIFI benchmarking Data
#====================================================================

hifi_benchmark_files <- dir("../pacbio_hifi/benchmarks", recursive=TRUE, full.names=TRUE, pattern=".tsv$")

hifi_bench <- as_tibble(plyr::ldply(hifi_benchmark_files, read.delim))

newCols <- c("rule_name",
             "threads",
             "read_type", 
             "assembly_type", 
             "assembly_tool", 
             "read_selection", 
             "prefix", 
             "bbduk_cov", 
             "bbduk_kmer", 
             "depth",             
             "polishdepth",
             "polishselect",
             "polishround")

hifi_bench[,newCols] <- NA

for( i in 1:length(hifi_benchmark_files)) {
  temp <- unlist(strsplit(hifi_benchmark_files[i], "/"))
  temp <- unlist(strsplit(temp, "_"))
  temp <- unlist(strsplit(temp, "\\."))
  hifi_bench[i,"rule_name"] <- temp[match("benchmarks", temp) +1]
  hifi_bench[i,"read_type"] <- "hifi"
  hifi_bench[i,"assembly_type"] <- temp[match("assemblytype", temp) +1]
  hifi_bench[i,"assembly_tool"] <- temp[match("assemblytool", temp) +1]
  hifi_bench[i,"read_selection"] <- temp[match("readselect", temp) +1]
  hifi_bench[i,"prefix"] <- temp[match("prefix", temp) +1]
  hifi_bench[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  hifi_bench[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  hifi_bench[i,"depth"] <- temp[match("depth", temp) +1]
  hifi_bench[i,"polishdepth"] <- temp[match("polishdepth", temp) +1]
  hifi_bench[i,"polishselect"] <- temp[match("polishselect", temp) +1]
  hifi_bench[i,"polishround"] <- temp[match("polishround", temp) +1]
}

hifi_bench$depth <- as.numeric(hifi_bench$depth)

#change rule_name flyegenome to flye.
hifi_bench$prefix <- str_replace(hifi_bench$prefix, "rice24kb", "24kb")
hifi_bench$prefix <- str_replace(hifi_bench$prefix, "SRR99694", "11kb")

```

# compare max rss for random genomes

```{r}
assemblers <- c("raven", "flye", "wtdbg2")
data1 <- subset(clr_bench, subset = rule_name %in% assemblers) 
data1 <- subset(data1, assembly_type == "genome") %>%
  subset(read_selection == "random") 

assemblers <- c("flye", "hifiasm")
data2 <- subset(hifi_bench, subset = rule_name %in% assemblers) 
data2 <- subset(data2, assembly_type == "genome") %>%
  subset(read_selection == "random")%>%
  subset(prefix == "24kb")

data3 <- subset(hifi_bench, subset = rule_name %in% assemblers) 
data3 <- subset(data3, assembly_type == "genome") %>%
  subset(read_selection == "random")%>%
  subset(prefix == "11kb")

ggplot(data1, aes(rule_name, max_rss, group = prefix, col=depth)) + 
  geom_point(size = 2, position = position_nudge(x=0)) + 
  xlab("Assembly Tool") +
  ylab("Max. Resident Set Size") +
  scale_y_continuous(labels = label_number(suffix = " Gb", scale = (1/1000))) +
  scale_colour_gradient("CLR\ncoverage",high = "#a54527", low = "#f4a187") +
  new_scale_color() +
  geom_point(data = data2, aes(color = depth), size = 2, position = position_nudge(x=-0.15)) +
  scale_colour_gradient("HiFi 24kb\ncoverage",high = "#463d58", low = "#d0ccd8") +
  new_scale_color() +
  geom_point(data = data3, aes(color = depth), size = 2, position = position_nudge(x=0.15)) +
  scale_colour_gradient("HiFi 11kb\ncoverage",high = "#388470", low = "#96d7c6") +
  theme(legend.position = "bottom",
        legend.text=element_text(size=7),
        legend.title = element_text(size=7),
        legend.key.width = unit(0.42,"cm"),
        legend.margin = margin(c(0.7,0.7,0.7,0.7))) +
  scale_fill_distiller() 

ggsave("images/allgenomes_max_rss.png",
         width = 5,
         height = 3,
         dpi = 300)

```

#Subset to get only assemblies completed on ronin.

```{r}
clr_bench$descriptor <- paste0(clr_bench$rule_name,
                               clr_bench$depth,
                               clr_bench$read_selection,
                               clr_bench$assembly_type)

hifi_bench$descriptor <- paste0(hifi_bench$rule_name,
                               hifi_bench$depth,
                               hifi_bench$read_selection,
                               hifi_bench$assembly_type)

clr_ronin <- c("flye10randomgenome",
               "flye25randomgenome",
               "raven50randomgenome",
               "wtdbg250randomgenome",
               "flye50randomgenome",
               "raven50longestgenome",
               "wtdbg250longestgenome",
               "flye50longestgenome",
               "raven75randomgenome",
               "wtdbg275randomgenome",
               "flye75randomgenome",
               "raven75longestgenome",
               "wtdbg275longestgenome",
               "flye75longestgenome",
               "raven100randomgenome",
               "wtdbg2100randomgenome",
               "flye100randomgenome",
               "raven100longestgenome",
               "wtdbg2100longestgenome",
               "flye100longestgenome",
               "raven125randomgenome",
               "wtdbg2125randomgenome",
               "flye125randomgenome",
               "raven125longestgenome",
               "wtdbg2125longestgenome",
               "flye125longestgenome",
               "raven150randomgenome",
               "wtdbg2150randomgenome",
               "flye150randomgenome",
               "raven150longestgenome",
               "wtdbg2150longestgenome")

hifi_11kbronin <- c("flye10randomgenome",
                "flye15randomgenome",
                "flye25randomgenome",
                "flye35randomgenome",
                "flye50randomgenome",
                "flye10longestgenome",
                "flye15longestgenome",
                "flye25longestgenome",
                "flye35longestgenome")
                
hifi_24kbronin <- c("hifiasm10randomgenome",
                "hifiasm15randomgenome",
                "hifiasm25randomgenome",
                "hifiasm35randomgenome",
                "hifiasm50randomgenome",
                "hifiasm60randomgenome",
                "hifiasm10longestgenome",
                "hifiasm15longestgenome",
                "hifiasm25longestgenome",
                "hifiasm35longestgenome",
                "hifiasm50longestgenome",
                "hifiasm60longestgenome",
                "flye10randomgenome",
                "flye15randomgenome",
                "flye25randomgenome",
                "flye35randomgenome",
                "flye50randomgenome",
                "flye60randomgenome",
                "flye10longestgenome",
                "flye15longestgenome",
                "flye25longestgenome",
                "flye35longestgenome",
                "flye50longestgenome",
                "flye60longestgenome")

clr_ronin_dat <- subset(clr_bench, descriptor %in% clr_ronin)

hifi_ronin24kb_dat <- subset(hifi_bench, prefix == "24kb") %>%
  subset(descriptor %in% hifi_24kbronin)

hifi_ronin11kb_dat <- subset(hifi_bench, prefix == "11kb") %>%
  subset(descriptor %in% hifi_11kbronin)

#join all three datasets together, add cores column = 48 and re-format to match benchmark data created from phoenix.

all_ronin_ass <- rbind(clr_ronin_dat, hifi_ronin24kb_dat, hifi_ronin11kb_dat)
all_ronin_ass$num_cores <- 48

test <- mutate(all_ronin_ass, core32 = s/num_cores*32)

```


##Processing phoenix log files for phoenix assemblies

========================================================================
========================================================================
Extracting benchmarking data from everything except canu
========================================================================
========================================================================

# Creating empty dataframes and selecting only complete jobs.

```{r}
path <- "../pacbio_clr/phoenix_bench/status.txt"
tempclr<- read_file(path) %>% 
  strsplit('\n')
completeRowsClr <- str_detect(tempclr[[1]],'COMPLETED')
tempclr <- tempclr[[1]][completeRowsClr]

path <- "../pacbio_hifi/phoenix_bench/status.txt"
temphifi<- read_file(path) %>% 
  strsplit('\n')
completeRowsHifi <- str_detect(temphifi[[1]],'COMPLETE')
temphifi <- temphifi[[1]][completeRowsHifi]

headers <- c("walltime","total_time","num_cores","max_memory","rule_name",
             "read_type", "assembly_type","assembly_tool","read_selection","prefix",
             "bbduk_cov","bbduk_kmer","depth","polishdepth","polishselect","polishround")

clr_all_results <- data.frame(matrix(NA, nrow=length(tempclr), ncol=length(headers)))
hifi_all_results=data.frame(matrix(NA, nrow=length(temphifi), ncol=length(headers)))

names(clr_all_results) <- headers
names(hifi_all_results) <- headers

#Populate Dataframe by parseing data from rows 

for( i in 1:length(tempclr)) {
  temp <- unlist(strsplit(tempclr[[i]], "/"))
  clr_all_results[i,"rule_name"] <- temp[match(".", temp) +1]
  temp <- unlist(strsplit(temp, ","))
  temp <- unlist(strsplit(temp, "="))
  clr_all_results[i,"read_type"] <- "clr"
  clr_all_results[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  temp <- temp[-1]
  temp <- unlist(strsplit(temp, "\\."))
  clr_all_results[i,"assembly_type"] <- temp[match("ass_type", temp) +1]
  clr_all_results[i,"assembly_tool"] <- temp[match("tool", temp) +1]
  clr_all_results[i,"read_selection"] <- temp[match("read_select", temp) +1]
  clr_all_results[i,"prefix"] <- temp[match("prefix", temp) +1]
  clr_all_results[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  clr_all_results[i,"depth"] <- temp[match("depth", temp) +1]
  clr_all_results[i,"polishdepth"] <- temp[match("polishdepth", temp) +1]
  clr_all_results[i,"polishselect"] <- temp[match("polishselect", temp) +1]
  clr_all_results[i,"polishround"] <- temp[match("polishround", temp) +1]
}

for( i in 1:length(temphifi)) {
  temp <- unlist(strsplit(temphifi[[i]], "/"))
  hifi_all_results[i,"rule_name"] <- temp[match(".", temp) +1]
  temp <- unlist(strsplit(temp, ","))
  temp <- unlist(strsplit(temp, "="))
  hifi_all_results[i,"read_type"] <- "hifi"
  hifi_all_results[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  temp <- temp[-1]
  temp <- unlist(strsplit(temp, "\\."))
  hifi_all_results[i,"assembly_type"] <- temp[match("ass_type", temp) +1]
  hifi_all_results[i,"assembly_tool"] <- temp[match("tool", temp) +1]
  hifi_all_results[i,"read_selection"] <- temp[match("read_select", temp) +1]
  hifi_all_results[i,"prefix"] <- temp[match("prefix", temp) +1]
  hifi_all_results[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  hifi_all_results[i,"depth"] <- temp[match("depth", temp) +1]
  hifi_all_results[i,"polishdepth"] <- temp[match("polishdepth", temp) +1]
  hifi_all_results[i,"polishselect"] <- temp[match("polishselect", temp) +1]
  hifi_all_results[i,"polishround"] <- temp[match("polishround", temp) +1]
}

```

#Add total_time data

```{r}
#calculate Walltime

findWalltime <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/walltime_elapsed.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  tempstring <- str_extract(data[[rowNo]], '[:digit:]?-?[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
    #num days
  days <- str_extract(tempstring, '^[:digit:]-') %>% str_extract('[:digit:]')
  days[is.na(days)] <- 0
  
  hours <- ((as.numeric(days))*24 + 
    (as.numeric(str_extract(tempstring, '[^|-][:digit:]'))) + 
    (as.numeric(str_extract(tempstring, ':[:digit:].:') %>% str_extract('[:digit:].')))/60 + 
    (as.numeric(str_extract(tempstring, ':[:digit:].$') %>% str_extract('[:digit:].')))/3600)

  return(sum(hours))
}

clr_all_results$walltime <- lapply(1:(nrow(clr_all_results)), FUN=findWalltime, type = "clr", completeRows = completeRowsClr)

hifi_all_results$walltime <- lapply(1:(nrow(hifi_all_results)), FUN=findWalltime, type = "hifi", completeRows = completeRowsHifi)
```

# Max memory resources

```{r}
#calculate max memory rsrcs.

findMaxMemory <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/max_memory.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  tempstring <- str_extract(data[[rowNo]], '([:digit:]+.[:digit:]+[:alpha:]/)')
  
  rawNum <- as.numeric(str_extract(tempstring, ".+?(?=[:alpha:])"))
  numZeros <- str_extract(tempstring, "([:alpha:])") 
  
  numZeros <- switch(numZeros, "K" = 0.001, "M" = 1, "G" = 1000)
  
  return(rawNum * numZeros)
}

clr_all_results$max_memory <- lapply(1:(nrow(clr_all_results)), FUN=findMaxMemory, type = "clr", completeRows = completeRowsClr)

hifi_all_results$max_memory <- lapply(1:(nrow(hifi_all_results)), FUN=findMaxMemory, type = "hifi", completeRows = completeRowsHifi)
```

```{r}
#extract Number of cores.
findNumCores <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/num_cores.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  tempstring <- str_extract(data[[rowNo]], '[:digit:]+$')
  return(tempstring)
}

clr_all_results$num_cores <- lapply(1:(nrow(clr_all_results)), FUN=findNumCores, type = "clr", completeRows = completeRowsClr)

hifi_all_results$num_cores <- lapply(1:(nrow(hifi_all_results)), FUN=findNumCores, type = "hifi", completeRows = completeRowsHifi)

```

```{r}
#extract total time (from submit to end)
findTotalTime <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/submit_time.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  submitTime <- str_extract(data[[rowNo]], '[:digit:]{4}-[:digit:]{2}-[:digit:]{2}T[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
  
  
path <- paste0("../pacbio_", type, "/phoenix_bench/end_time.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
    data <- data[[1]][completeRows]
  endTime <- str_extract(data[[rowNo]], '[:digit:]{4}-[:digit:]{2}-[:digit:]{2}T[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
  totalTime <- ymd_hms(endTime) - ymd_hms(submitTime)
  
  return(totalTime / dhours(1))
}

clr_all_results$total_time <- lapply(1:(nrow(clr_all_results)), FUN=findTotalTime, type = "clr", completeRows = completeRowsClr)

hifi_all_results$total_time <- lapply(1:(nrow(hifi_all_results)), FUN=findTotalTime, type = "hifi", completeRows = completeRowsHifi)

```

```{r}
all_ronin_ass 
hifi_all_results
clr_all_results
phoenix <- rbind(hifi_all_results, clr_all_results)
phoenix <- subset(phoenix, assembly_type == "genome")
phoenix <- subset(phoenix, rule_name %in% c("flye","wtdbg2","raven","canu","hicanu","hifiasm"))

#subset ronin data to walltime + num_cores, assembly_type, ass tool, read selection, prefix, depth
ronin_cols <-   c("s", "num_cores","assembly_type","rule_name","read_selection","prefix","depth")
phoenix_cols <- c("walltime", "num_cores","assembly_type","rule_name","read_selection", "prefix",
                  "depth")

phoenix <- phoenix[,phoenix_cols] 
ronin <- all_ronin_ass[,ronin_cols]

```


#Calculating max time for flye on clr and hifi. Don't really need yet.

```{r}
hifi <- hifi_all_results
hifi$num_cores <- as.numeric(hifi$num_cores)
hifi$walltime <- as.numeric(hifi$walltime)
hifi <- hifi %>% mutate(su = walltime * num_cores)

temp <- sum(subset(hifi,rule_name == "pbindex")$su)
temp <- temp + sum(subset(hifi,rule_name == "ccs")$su)
temp <- temp + sum(subset(hifi,rule_name == "pbmerge")$su)
temp <- temp + sum(subset(hifi,rule_name == "pbmerge_sample")$su)
temp <- temp + (14707/(60*60)*48)
Flye_hifi_11kb_50x_random_SU_hrs <- temp

clr <- clr_all_results
clr$num_cores <- as.numeric(clr$num_cores)
clr$walltime <- as.numeric(clr$walltime)
clr <- clr %>% mutate(su = walltime * num_cores)
subset(clr,rule_name == "flye")
Flye_clr_30kb_150x_random_SU_hrs <- 45334/(60*60)*48

#Flye 150x random clr genome on ronin = 45334 seconds at 48 cores
#Flye 50x srr99694 was done on ronin - 14707seconds and 48 cores

```


Join together, format and add columns where necessary

```{r}
clr_results <- rbind(clr_canu_results, clr_all_results)
hifi_results <- rbind(hifi_canu_results, hifi_all_results)

clr_results <- clr_results %>% mutate(
  total_time_min = as.numeric(total_time) * 60)
hifi_results <- hifi_results %>% mutate(
  total_time_min = as.numeric(total_time) * 60)

clr_results <- clr_results %>% mutate(
  walltime_min = as.numeric(walltime) * 60)
hifi_results <- hifi_results %>% mutate(
  walltime_min = as.numeric(walltime) * 60)

clr_results$depth <- as.factor(as.numeric(clr_results$depth))
clr_results$read_selection <- factor(clr_results$read_selection)
hifi_results$depth <- as.factor(as.numeric(hifi_results$depth))
hifi_results$read_selection <- factor(hifi_results$read_selection)
```


