---
title: "Busco"
author: "Chelsea Matthews"
date: "11 May 2020"
output: 
  html_document:
      code_folding: "show"
      number_sections: TRUE
      toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
											results = "asis",
											message = FALSE, warning = FALSE,
											error = FALSE)
```

Code for extracting busco data

chelsea@Chelseas-Laptop:~/fast_dir/pacbio_hifi$ rsync -amv --ignore-existing --include ='/*/results/*/full_table.tsv' --exclude='first_failed_busco/' --exclude='*/results/run_poales_odb10/hmmer_output' --exclude='*/results/run_poales_odb10/busco_sequences' --exclude='*/results/run_poales_odb10/blast_output' --exclude='*/results/run_poales_odb10/augustus_output' --exclude='*/results/logs' --exclude='*/results/blast_db' --exclude='*/results/run_poales_odb10/short*' --exclude='*/results/run_poales_odb10/missing*' --exclude='*/results/short*' phoenix:/home/a1761942/fast_dir/pacbio_hifi/busco .

Libraries

```{r}
library(plyr)
library(tidyverse)
library(ggplot2)
library(grImport)
library(XML)
library(kableExtra)
library(cluster)
library(purrr)
library(data.table)
library(ggpubr)
library(scales)
library(viridis)
library(dplyr)
library(cowplot) 
library(egg)
library(fuzzyjoin)
```


Get file paths
```{r}
busco_hifi_path <- dir("../pacbio_hifi/busco", recursive=TRUE, full.names=TRUE, pattern="full_table.tsv$")

busco_clr_path <- dir("../pacbio_clr/busco", recursive=TRUE, full.names=TRUE, pattern="full_table.tsv$")

#get rid of polished data
busco_clr_path <- busco_clr_path[!str_detect(busco_clr_path,pattern="polish")]
```

HIFI DATA PROCESSING
#make an empty list and fill it with data
```{r}
hifi <- vector(mode = "list", length = length(busco_hifi_path))

#read in data
for( i in 1:length(busco_hifi_path)) {
  temp <- read.delim(busco_hifi_path[[i]], header=FALSE)
  temp <- tail(temp,-3)
  temp <- select(temp, V1,V2)
  temp <- unique(temp)
  temp <- select(temp, V2)
  temp <- as.factor(temp$V2)
  temp <- factor(temp)
  hifi[[i]] <- as.data.frame(table(temp))
  
}

names(hifi) <- busco_hifi_path

```

#Create four separate data frames, one each for complete, fragmented, fragmented and missing
Add coverage, longest/random, sampleName, tool to each entry

```{r}
#create four dataframes 
complete_h <- data.frame(matrix(NA, nrow=length(busco_hifi_path), ncol=5))
duplicated_h <- data.frame(matrix(NA, nrow=length(busco_hifi_path), ncol=5))
fragmented_h <- data.frame(matrix(NA, nrow=length(busco_hifi_path), ncol=5))
missing_h <- data.frame(matrix(NA, nrow=length(busco_hifi_path), ncol=5))
#all <- data.frame(matrix(NA, nrow=(length(busco_hifi_path)*4), ncol=8))

for( i in 1:length(busco_hifi_path)) {
  temp <- names(hifi[i])
  temp <- unlist(strsplit(temp, '_'))
  temp <- unlist(strsplit(temp,"/"))

  depth <- temp[match("depth", temp) +1]
  readselect <- temp[match("readselect", temp) +1]
  prefix <- temp[match("prefix", temp) +1]
  tool <- temp[match("assemblytool", temp) +1]
    
  complete_h[i,1] <- hifi[[i]][1,2]
  complete_h[i,2] <- depth
  complete_h[i,3] <- readselect
  complete_h[i,4] <- prefix
  complete_h[i,5] <- tool

  duplicated_h[i,1] <- hifi[[i]][2,2]
  duplicated_h[i,2] <- depth
  duplicated_h[i,3] <- readselect
  duplicated_h[i,4] <- prefix
  duplicated_h[i,5] <- tool
  
  fragmented_h[i,1] <- hifi[[i]][3,2]
  fragmented_h[i,2] <- depth
  fragmented_h[i,3] <- readselect
  fragmented_h[i,4] <- prefix
  fragmented_h[i,5] <- tool  
  
  missing_h[i,1] <- hifi[[i]][4,2]
  missing_h[i,2] <- depth
  missing_h[i,3] <- readselect
  missing_h[i,4] <- prefix
  missing_h[i,5] <- tool
  
}


complete_h$uniqueName <- paste0(complete_h$X4,"_",complete_h$X5,"_",complete_h$X3)
duplicated_h$uniqueName <- paste0(duplicated_h$X4,"_",duplicated_h$X5,"_",duplicated_h$X3)
fragmented_h$uniqueName <- paste0(fragmented_h$X4,"_",fragmented_h$X5,"_",fragmented_h$X3)
missing_h$uniqueName <- paste0(missing_h$X4,"_",missing_h$X5,"_",missing_h$X3)
```


```{r}
ggplot(fragmented_h, aes(x = uniqueName, X2, fill= X1)) + 
  geom_tile() + 
  theme_classic()
```

Shaping data for bar plots

```{r}
#Add new column to each of the existing dataframes
complete_h$status <- "complete"
missing_h$status <- "missing"
duplicated_h$status <- "duplicated"
fragmented_h$status <- "fragmented"

#Add new name col
complete_h$uniqueName2 <- paste0(complete_h$X4,"_",complete_h$X5,"_",complete_h$X3,"_",complete_h$X2)
duplicated_h$uniqueName2 <- paste0(duplicated_h$X4,"_",duplicated_h$X5,"_",duplicated_h$X3, "_",duplicated_h$X2)
fragmented_h$uniqueName2 <- paste0(fragmented_h$X4,"_",fragmented_h$X5,"_",fragmented_h$X3,"_",fragmented_h$X2)
missing_h$uniqueName2 <- paste0(missing_h$X4,"_",missing_h$X5,"_",missing_h$X3,"_",missing_h$X2)

#Add complete and fragmented together in the complete column
complete_h$X1 <- complete_h$X1 + duplicated_h$X1

all_hifi <- rbind(complete_h,duplicated_h,fragmented_h,missing_h)
all_hifi$percent <- all_hifi$X1/4896
```

CLR DATA PROCESSING

#make an empty list and fill it with data
```{r}
clr <- vector(mode = "list", length = length(busco_clr_path))

#read in data
for( i in 1:length(busco_clr_path)) {
  temp <- read.delim(busco_clr_path[[i]], header=FALSE)
  temp <- tail(temp,-3)
  temp <- select(temp, V1,V2)
  temp <- unique(temp)
  temp <- select(temp, V2)
  temp <- as.factor(temp$V2)
  temp <- factor(temp)
  clr[[i]] <- as.data.frame(table(temp))
  
}

names(clr) <- busco_clr_path

```

#Create four separate data frames, one each for complete, fragmented, fragmented and missing
Add coverage, longest/random, sampleName, tool to each entry.

```{r}
#create four dataframes 
complete_c <- data.frame(matrix(NA, nrow=length(busco_clr_path), ncol=5))
duplicated_c <- data.frame(matrix(NA, nrow=length(busco_clr_path), ncol=5))
fragmented_c <- data.frame(matrix(NA, nrow=length(busco_clr_path), ncol=5))
missing_c <- data.frame(matrix(NA, nrow=length(busco_clr_path), ncol=5))
#all <- data.frame(matrix(NA, nrow=(length(busco_hifi_path)*4), ncol=8))

for( i in 1:length(busco_clr_path)) {
  temp <- names(clr[i])
  temp <- unlist(strsplit(temp, '_'))
  temp <- unlist(strsplit(temp,"/"))

  depth <- temp[match("depth", temp) +1]
  readselect <- temp[match("readselect", temp) +1]
  prefix <- temp[match("prefix", temp) +1]
  tool <- temp[match("assemblytool", temp) +1]
    
  complete_c[i,1] <- clr[[i]][1,2]
  complete_c[i,2] <- depth
  complete_c[i,3] <- readselect
  complete_c[i,4] <- prefix
  complete_c[i,5] <- tool

  duplicated_c[i,1] <- clr[[i]][2,2]
  duplicated_c[i,2] <- depth
  duplicated_c[i,3] <- readselect
  duplicated_c[i,4] <- prefix
  duplicated_c[i,5] <- tool
  
  fragmented_c[i,1] <- clr[[i]][3,2]
  fragmented_c[i,2] <- depth
  fragmented_c[i,3] <- readselect
  fragmented_c[i,4] <- prefix
  fragmented_c[i,5] <- tool  
  
  missing_c[i,1] <- clr[[i]][4,2]
  missing_c[i,2] <- depth
  missing_c[i,3] <- readselect
  missing_c[i,4] <- prefix
  missing_c[i,5] <- tool
  
}

```

#Create new column with unique names

```{r}
complete_c$uniqueName <- paste0(complete_c$X4,"_",complete_c$X5,"_",complete_c$X3)
duplicated_c$uniqueName <- paste0(duplicated_c$X4,"_",duplicated_c$X5,"_",duplicated_c$X3)
fragmented_c$uniqueName <- paste0(fragmented_c$X4,"_",fragmented_c$X5,"_",fragmented_c$X3)
missing_c$uniqueName <- paste0(missing_c$X4,"_",missing_c$X5,"_",missing_c$X3)
```


```{r}
ggplot(fragmented_c, aes(x = uniqueName, X2, fill= X1)) + 
  geom_tile() + 
  theme_classic()
```

Shaping data for bar plots

```{r}
#Add new column to each of the existing dataframes
complete_c$status <- "complete"
missing_c$status <- "missing"
duplicated_c$status <- "duplicated"
fragmented_c$status <- "fragmented"

#Add new name col
complete_c$uniqueName2 <- paste0(complete_c$X4,"_",complete_c$X5,"_",complete_c$X3,"_",complete_c$X2)
duplicated_c$uniqueName2 <- paste0(duplicated_c$X4,"_",duplicated_c$X5,"_",duplicated_c$X3, "_",duplicated_c$X2)
fragmented_c$uniqueName2 <- paste0(fragmented_c$X4,"_",fragmented_c$X5,"_",fragmented_c$X3,"_",fragmented_c$X2)
missing_c$uniqueName2 <- paste0(missing_c$X4,"_",missing_c$X5,"_",missing_c$X3,"_",missing_c$X2)

#Add complete and fragmented together in the complete column
complete_c$X1 <- complete_c$X1 + fragmented_c$X1

all_clr <- rbind(complete_c,duplicated_c,fragmented_c,missing_c)
all_clr$percent <- all_clr$X1/4896

all <- rbind(all_clr,all_hifi)

all <- all %>% 
  mutate(assembly_type = X4)

all$assembly_type <- str_replace(all$assembly_type, "SRR99694", "HiFi")
all$assembly_type <- str_replace(all$assembly_type, "rice24kb", "HiFi")
all$assembly_type <- str_replace(all$assembly_type, "m64015", "CLR")

all$X2 <- factor(all$X2, levels = c("10","15","25","35","50","60","75","100","125","150"))

```

Bar Graphs - 4896 genes in list.

```
names <- c("rice24kb_canu_random_10","rice24kb_canu_random_15",
           "rice24kb_canu_random_25","rice24kb_canu_random_35",
           "rice24kb_canu_random_50")

test <- subset(all,uniqueName2 %in% names)

ggplot(data=test, aes(x=uniqueName2, y=percent, fill=status)) +
    geom_bar(stat="identity") +
  coord_flip() +
  scale_fill_manual(values=c("dodgerblue2", "dodgerblue4", "gold2","firebrick3")) 
  
```

#Line graphs 

```{r}
#all$colourFactor <- as.factor(paste0(all$X5,all$assembly_type))

myColors <- c("orangered3","darkgoldenrod3","slateblue3","plum3","gray54","green4")

names(myColors) <- c("canu","flye","hicanu","hifiasm","raven","wtdbg2")
colScale <- scale_colour_manual(name = "Assembly Tool", values = myColors)

#min_complete <- 4425
min_complete <- 1650
max_complete <- 4600

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "m64015") %>%
  subset(status == "complete")

completeCLR <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  ylab("Complete BUSCOs") + 
    expand_limits(y=c(min_complete,max_complete)) + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "SRR99694") %>%
  subset(status == "complete")
  
complete11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())+ 
  expand_limits(y=c(min_complete,max_complete))

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "rice24kb") %>%
  subset(status == "complete")

complete24 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) + 
  expand_limits(y=c(min_complete,max_complete))

#duplicated
min_duplicated <- 20
max_duplicated <- 700

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "m64015") %>%
  subset(status == "duplicated")

duplicatedCLR <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  ylab("Duplicated BUSCOs") + 
  expand_limits(y=c(min_duplicated,max_duplicated)) +
  scale_y_log10() + 
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank())

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "SRR99694") %>%
  subset(status == "duplicated")
  
duplicated11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())+ 
  expand_limits(y=c(min_duplicated,max_duplicated)) +
    scale_y_log10()

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "rice24kb") %>%
  subset(status == "duplicated")

duplicated24 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) + 
  expand_limits(y=c(min_duplicated,max_duplicated)) +
    scale_y_log10()

#Fragmented

min_fragmented <- 50
max_fragmented <- 250

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "m64015") %>%
  subset(status == "fragmented")

fragmentedCLR <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  ylab("Fragmented BUSCOs") + 
  expand_limits(y=c(min_fragmented,max_fragmented)) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank())

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "SRR99694") %>%
  subset(status == "fragmented")
  
fragmented11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())+ 
  expand_limits(y=c(min_fragmented,max_fragmented))

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "rice24kb") %>%
  subset(status == "fragmented")

fragmented24 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) + 
  expand_limits(y=c(min_fragmented,max_fragmented)) 

#missing

min_missing <- 100
max_missing <- 4000

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "m64015") %>%
  subset(status == "missing")

missingCLR <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  ylab("Missing BUSCOs") + 
  scale_y_log10(breaks = c(100,300,1000,3000)) +
  expand_limits(y=c(min_missing,max_missing))

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "SRR99694") %>%
  subset(status == "missing")
  
missing11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())+ 
  scale_y_log10(breaks = c(100,300,1000,3000))+
    expand_limits(y=c(min_missing,max_missing))

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "rice24kb") %>%
  subset(status == "missing")

missing24 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) + 
    scale_y_log10(breaks = c(100,300,1000,3000))+
  expand_limits(y=c(min_missing,max_missing)) 

```



```{r}

dummy <- ggplot(all, aes(x = X2, y = X1, group = X5)) +
  geom_line(aes(color = X5)) + 
colScale +
  theme_minimal()

legend <- get_legend(
  dummy + 
    guides(color = guide_legend(nrow = 2)) +
    theme(legend.position = "bottom")
  )

topSpace <- 0.5
bottomSpace <- 0.2
rightSpace <- 0.2
leftSpace <- 0.2

myPlot <- egg::ggarrange(
  completeCLR + theme(legend.position="none",
                      plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")),
  complete11 + theme(legend.position="none",
                     plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")),
  complete24 + theme(legend.position="none",
                     plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")), 
  duplicatedCLR + theme(legend.position="none"),
  duplicated11 + theme(legend.position="none"),
  duplicated24 + theme(legend.position="none"),  
  fragmentedCLR + theme(legend.position="none"),
  fragmented11 + theme(legend.position="none"),
  fragmented24 + theme(legend.position="none"),  
  missingCLR + theme(legend.position="none"),
  missing11 + theme(legend.position="none"),
  missing24 + theme(legend.position="none"),  
  widths = c(0.39,0.31,0.36),
  labels = c("       CLR","HiFi 11kb","HiFi 24kb","","","","","","","","",""))

endPlot <- plot_grid(myPlot, legend, nrow = 2, rel_heights = c(1, .12))

ggsave("images/busco/busco_scores.png",
         width = 7,
         height = 8,
         dpi = 300)




```

Busco graphs for presentation

```{r}
min_complete <- 1650
max_complete <- 4600

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "m64015") %>%
  subset(status == "complete")

completeCLR <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  ylab("Complete BUSCOs") + 
    expand_limits(y=c(min_complete,max_complete)) + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "SRR99694") %>%
  subset(status == "complete")
  
complete11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())+ 
  expand_limits(y=c(min_complete,max_complete))

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "rice24kb") %>%
  subset(status == "complete")

complete24 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) + 
  expand_limits(y=c(min_complete,max_complete))

#duplicated
min_duplicated <- 20
max_duplicated <- 700

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "m64015") %>%
  subset(status == "duplicated")

duplicatedCLR <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  ylab("Duplicated BUSCOs") + 
  expand_limits(y=c(min_duplicated,max_duplicated)) +
  scale_y_log10()

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "SRR99694") %>%
  subset(status == "duplicated")
  
duplicated11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  expand_limits(y=c(min_duplicated,max_duplicated)) +
    scale_y_log10()+ 
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

dat <- subset(all, X3 == "random") %>%
  subset(X4 == "rice24kb") %>%
  subset(status == "duplicated")

duplicated24 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  expand_limits(y=c(min_duplicated,max_duplicated)) +
    scale_y_log10()+ 
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

myPlot <- egg::ggarrange(
  completeCLR + theme(legend.position="none",
                      plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")),
  complete11 + theme(legend.position="none",
                     plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")),
  complete24 + theme(legend.position="none",
                     plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")), 
  duplicatedCLR + theme(legend.position="none"),
  duplicated11 + theme(legend.position="none"),
  duplicated24 + theme(legend.position="none"),
  widths = c(0.39,0.31,0.36),
  labels = c("          CLR","HiFi 11kb","HiFi 24kb","","",""),
  label.args = list(gp=gpar(fontface = "plain", fontfamily = "Simplex Roman")))

endPlot <- plot_grid(myPlot, nrow = 1, rel_heights = c(1))

ggsave("images/busco/busco_complete_n_duplicated.png",
         width = 7,
         height = 4,
         dpi = 300)

myPlot <- egg::ggarrange(
  fragmentedCLR + theme(legend.position="none",
                      plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")),
  fragmented11 + theme(legend.position="none",
                     plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")),
  fragmented24 + theme(legend.position="none",
                     plot.margin = unit(c(topSpace, rightSpace, bottomSpace, leftSpace), "cm")), 
  missingCLR + theme(legend.position="none"),
  missing11 + theme(legend.position="none"),
  missing24 + theme(legend.position="none"),
  widths = c(0.39,0.31,0.36),
  labels = c("          CLR","HiFi 11kb","HiFi 24kb","","",""),
  label.args = list(gp=gpar(fontface = "plain", fontfamily = "Simplex Roman")))

endPlot <- plot_grid(myPlot, nrow = 1, rel_heights = c(1))

ggsave("images/busco/busco_fragmented_n_missing.png",
         width = 7,
         height = 4,
         dpi = 300)

endLeg <- plot_grid(legend, nrow = 1, rel_heights = c(1))

ggsave("images/busco/legend.png",
         width = 4,
         height = 0.7,
         dpi = 300)



```

