---
title: "canu_data_extraction"
author: "Chelsea Matthews"
date: "9 April 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(magrittr)
library(ggplot2)
library(plyr)
library(tidyverse)
library(ggplot2)
library(grImport)
library(XML)
library(kableExtra)
library(cluster)
library(purrr)
library(data.table)
library(ggpubr)
library(scales)
library(viridis)
library(dplyr)
library(cowplot) 
library(egg) 
library(ggnewscale)
library(readr)
library(lubridate)
library(magrittr)
```

# Canu Benchmarking

#find all folders in the benchcanu folders 

```{r}
clr_canu_bench <- list.dirs(path = "../pacbio_clr/benchcanu", full.names = TRUE, recursive = FALSE)

hifi_canu_bench <- list.dirs(path = "../pacbio_hifi/benchcanu", full.names = TRUE, recursive = FALSE)

```

# Create empty tibble with appropriate column headers

Note the following units:
walltime: actual processing hours 
total_time: submit to end hours
max_memory: Mb

```{r}

headers <- c("walltime","total_time","num_cores","max_memory","rule_name",
             "read_type", "assembly_type","assembly_tool","read_selection","prefix",
             "bbduk_cov","bbduk_kmer","depth")

clr_canu_results <- data.frame(matrix(NA, nrow=length(clr_canu_bench), ncol=length(headers)))
hifi_canu_results=data.frame(matrix(NA, nrow=length(hifi_canu_bench), ncol=length(headers)))

#headers <- c("walltime","total_time","max_rss","max_vms","max_uss","max_pss","io_in",
#             "io_out","mean_load","rule_name","threads","read_type","assembly_type",
#             "assembly_tool","read_selection","prefix","bbduk_cov","bbduk_kmer","depth")


names(clr_canu_results) <- headers
names(hifi_canu_results) <- headers

```

# Populate results tables with data describing the type of assembly (eg, coverage, ass type, ass tool etc.)

```{r}
lengthTest <- length(clr_canu_bench) > 1
if (lengthTest){
  for( i in 1:length(clr_canu_bench)) {
    temp <- unlist(strsplit(clr_canu_bench[i], "/"))
    temp <- unlist(strsplit(temp, "_"))
    temp <- unlist(strsplit(temp, "\\."))
    clr_canu_results[i,"read_type"] <- temp[match("pacbio", temp) +1]
    clr_canu_results[i,"assembly_type"] <- temp[match("assemblytype", temp) +1]
    clr_canu_results[i,"assembly_tool"] <- temp[match("assemblytool", temp) +1]
    clr_canu_results[i,"read_selection"] <- temp[match("readselect", temp) +1]
    clr_canu_results[i,"prefix"] <- temp[match("prefix", temp) +1]
    clr_canu_results[i,"bbduk_cov"] <- paste0("0.",temp[match("cov", temp) +2])
    clr_canu_results[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
    clr_canu_results[i,"depth"] <- temp[match("depth", temp) +1]
    clr_canu_results[i,"rule_name"] <- temp[match("assemblytool", temp) +1]
  }
}

lengthTest <- length(hifi_canu_bench)>1
if (lengthTest) {
  for( i in 1:length(hifi_canu_bench)) {
    temp <- unlist(strsplit(hifi_canu_bench[i], "/"))
    temp <- unlist(strsplit(temp, "_"))
    temp <- unlist(strsplit(temp, "\\."))
    hifi_canu_results[i,"read_type"] <- temp[match("pacbio", temp) +1]
    hifi_canu_results[i,"assembly_type"] <- temp[match("assemblytype", temp) +1]
    hifi_canu_results[i,"assembly_tool"] <- temp[match("assemblytool", temp) +1]
    hifi_canu_results[i,"read_selection"] <- temp[match("readselect", temp) +1]
    hifi_canu_results[i,"prefix"] <- temp[match("prefix", temp) +1]
    hifi_canu_results[i,"bbduk_cov"] <- paste0("0.",temp[match("cov", temp) +2])
    hifi_canu_results[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
    hifi_canu_results[i,"depth"] <- temp[match("depth", temp) +1]
    hifi_canu_results[i,"rule_name"] <- temp[match("assemblytool", temp) +1]
  }
}


```

# Calculate the max memory usage 

Requires both max_memory and num_cores

```{r}
convertToMb <- function(str){
  rawNum <- as.numeric(str_extract(str, ".+?(?=[:alpha:])"))
  numZeros <- str_extract(str, "([:alpha:])") 
  
  numZeros <- switch(numZeros, "K" = 0.001, "M" = 1, "G" = 1000)
  return(numZeros*rawNum)
}

# Function to find the maximum memory per node (number of cores * max memory per core)
findMaxMem <- function(rowNo,benchData){
  
  path <- paste0(benchData[rowNo], "/max_memory.txt")
  tempstring <- read_file(path) %>% 
    strsplit('\n')
  tempstring <- str_extract(tempstring[[1]], '([0-9]*.[0-9]*[:alpha:]/core)') 
  memInMb <- lapply(tempstring,convertToMb)
  memInMb <- as.numeric(memInMb)

  path <- paste0(benchData[rowNo],"/num_cores.txt")
  tempstring <- read_file(path) %>%
    strsplit('\n')
  tempstring <- as.numeric(str_extract(tempstring[[1]], '([0-9]+$)'))

  totMemPerJob <- tempstring*memInMb

  return(max(totMemPerJob))
  
}

lengthTest <- length(clr_canu_bench)>1
if (lengthTest){
  clr_canu_results$max_memory <- lapply(1:length(clr_canu_bench), FUN=findMaxMem, benchData = clr_canu_bench)
} 

lengthTest <- length(hifi_canu_bench)>1
if (lengthTest){
  hifi_canu_results$max_memory <- lapply(1:length(hifi_canu_bench), FUN=findMaxMem, benchData = hifi_canu_bench)
} 


```

# Extract runtime in seconds (from start to finish)
I want to record both the time from start to finish and the total runtime. 
This section will calculate processing time not including wait time. 

```{r}
findWalltimeElapsed <- function(rowNo,benchData){
  
  path <- paste0(benchData[rowNo], "/walltime_elapsed.txt")
  tempstring <- read_file(path) %>% 
    strsplit('\n')
  tempstring <- str_extract(tempstring[[1]], '[:digit:]?-?[:digit:]+:[:digit:]+:[:digit:]+') 

  #num days
  days <- str_extract(tempstring, '^[:digit:]-') %>% str_extract('[:digit:]')
  days[is.na(days)] <- 0
  
  hours <- ((as.numeric(days))*24 + 
    (as.numeric(str_extract(tempstring, '[^|-][:digit:]'))) + 
    (as.numeric(str_extract(tempstring, ':[:digit:].:') %>% str_extract('[:digit:].')))/60 + 
    (as.numeric(str_extract(tempstring, ':[:digit:].$') %>% str_extract('[:digit:].')))/3600)
  
  return(sum(hours))
}

lengthTest <- length(clr_canu_bench)>1
if (lengthTest){
  clr_canu_results$walltime <- lapply(1:length(clr_canu_bench), FUN=findWalltimeElapsed, benchData = clr_canu_bench)
} 

lengthTest <- length(hifi_canu_bench)>1
if (lengthTest){
  hifi_canu_results$walltime <- lapply(1:length(hifi_canu_bench), FUN=findWalltimeElapsed, benchData = hifi_canu_bench)
} 


```

# Total time from start to finish 

uses submit_time and end_time. 

```{r}

findTotalTime <- function(rowNo, benchData){
  
  path <- paste0(benchData[rowNo], "/submit_time.txt")
  tempstring <- read_file(path) %>% 
    strsplit('\n')
  tempstring <- str_extract(tempstring[[1]], '[:digit:]{4}-[:digit:]{2}-[:digit:]{2}T[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 

  submitTime <- min(tempstring)
  
    path <- paste0(benchData[rowNo], "/end_time.txt")
  tempstring <- read_file(path) %>% 
    strsplit('\n')
  tempstring <- str_extract(tempstring[[1]], '[:digit:]{4}-[:digit:]{2}-[:digit:]{2}T[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
  
  endTime <- max(tempstring)
  totalTime <- ymd_hms(endTime) - ymd_hms(submitTime)
  return(totalTime / dhours(1))
}

lengthTest <- length(clr_canu_bench)>1
if (lengthTest){
  clr_canu_results$total_time <- lapply(1:length(clr_canu_bench), FUN=findTotalTime, benchData = clr_canu_bench)
} 

lengthTest <- length(hifi_canu_bench)>1
if (lengthTest){
  hifi_canu_results$total_time <- lapply(1:length(hifi_canu_bench), FUN=findTotalTime, benchData = hifi_canu_bench)
} 
```


```{r eval=FALSE}


```

========================================================================
========================================================================
Extracting benchmarking data from everything except canu
========================================================================
========================================================================

# Creating empty dataframes and selecting only complete jobs.

```{r}
path <- "../pacbio_clr/phoenix_bench/status.txt"
tempclr<- read_file(path) %>% 
  strsplit('\n')
completeRowsClr <- str_detect(tempclr[[1]],'COMPLETED')
tempclr <- tempclr[[1]][completeRowsClr]

path <- "../pacbio_hifi/phoenix_bench/status.txt"
temphifi<- read_file(path) %>% 
  strsplit('\n')
completeRowsHifi <- str_detect(temphifi[[1]],'COMPLETE')
temphifi <- temphifi[[1]][completeRowsHifi]

headers <- c("walltime","total_time","num_cores","max_memory","rule_name",
             "read_type", "assembly_type","assembly_tool","read_selection","prefix",
             "bbduk_cov","bbduk_kmer","depth")

clr_all_results <- data.frame(matrix(NA, nrow=length(tempclr), ncol=length(headers)))
hifi_all_results=data.frame(matrix(NA, nrow=length(temphifi), ncol=length(headers)))

names(clr_all_results) <- headers
names(hifi_all_results) <- headers

#Populate Dataframe by parseing data from rows 

for( i in 1:length(tempclr)) {
  temp <- unlist(strsplit(tempclr[[i]], "/"))
  clr_all_results[i,"rule_name"] <- temp[match(".", temp) +1]
  temp <- unlist(strsplit(temp, ","))
  temp <- unlist(strsplit(temp, "="))
  clr_all_results[i,"read_type"] <- "clr"
  clr_all_results[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  temp <- temp[-1]
  temp <- unlist(strsplit(temp, "\\."))
  clr_all_results[i,"assembly_type"] <- temp[match("ass_type", temp) +1]
  clr_all_results[i,"assembly_tool"] <- temp[match("tool", temp) +1]
  clr_all_results[i,"read_selection"] <- temp[match("read_select", temp) +1]
  clr_all_results[i,"prefix"] <- temp[match("prefix", temp) +1]
  clr_all_results[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  clr_all_results[i,"depth"] <- temp[match("depth", temp) +1]
}

for( i in 1:length(temphifi)) {
  temp <- unlist(strsplit(temphifi[[i]], "/"))
  hifi_all_results[i,"rule_name"] <- temp[match(".", temp) +1]
  temp <- unlist(strsplit(temp, ","))
  temp <- unlist(strsplit(temp, "="))
  hifi_all_results[i,"read_type"] <- "hifi"
  hifi_all_results[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  temp <- temp[-1]
  temp <- unlist(strsplit(temp, "\\."))
  hifi_all_results[i,"assembly_type"] <- temp[match("ass_type", temp) +1]
  hifi_all_results[i,"assembly_tool"] <- temp[match("tool", temp) +1]
  hifi_all_results[i,"read_selection"] <- temp[match("read_select", temp) +1]
  hifi_all_results[i,"prefix"] <- temp[match("prefix", temp) +1]
  hifi_all_results[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  hifi_all_results[i,"depth"] <- temp[match("depth", temp) +1]
}

```

#Add total_time data

```{r}
#calculate Walltime

findWalltime <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/walltime_elapsed.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  tempstring <- str_extract(data[[rowNo]], '[:digit:]?-?[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
    #num days
  days <- str_extract(tempstring, '^[:digit:]-') %>% str_extract('[:digit:]')
  days[is.na(days)] <- 0
  
  hours <- ((as.numeric(days))*24 + 
    (as.numeric(str_extract(tempstring, '[^|-][:digit:]'))) + 
    (as.numeric(str_extract(tempstring, ':[:digit:].:') %>% str_extract('[:digit:].')))/60 + 
    (as.numeric(str_extract(tempstring, ':[:digit:].$') %>% str_extract('[:digit:].')))/3600)

  return(sum(hours))
}

clr_all_results$walltime <- lapply(1:(nrow(clr_all_results)), FUN=findWalltime, type = "clr", completeRows = completeRowsClr)

hifi_all_results$walltime <- lapply(1:(nrow(hifi_all_results)), FUN=findWalltime, type = "hifi", completeRows = completeRowsHifi)
```

# Max memory resources

```{r}
#calculate max memory rsrcs.

findMaxMemory <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/max_memory.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  tempstring <- str_extract(data[[rowNo]], '([:digit:]+.[:digit:]+[:alpha:]/)')
  
  rawNum <- as.numeric(str_extract(tempstring, ".+?(?=[:alpha:])"))
  numZeros <- str_extract(tempstring, "([:alpha:])") 
  
  numZeros <- switch(numZeros, "K" = 0.001, "M" = 1, "G" = 1000)
  
  return(rawNum * numZeros)
}

clr_all_results$max_memory <- lapply(1:(nrow(clr_all_results)), FUN=findMaxMemory, type = "clr", completeRows = completeRowsClr)

hifi_all_results$max_memory <- lapply(1:(nrow(hifi_all_results)), FUN=findMaxMemory, type = "hifi", completeRows = completeRowsHifi)
```

```{r}
#extract Number of cores.
findNumCores <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/num_cores.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  tempstring <- str_extract(data[[rowNo]], '[:digit:]+$')
  return(tempstring)
}

df <- data.frame(matrix(unlist(l), nrow=length(l), byrow=T))
temp <- lapply(1:(nrow(clr_all_results)), FUN=findNumCores, type = "clr", completeRows = completeRowsClr)

clr_all_results$num_cores <- data.frame(matrix(unlist(temp), nrow = length(temp), byrow = T))

as.data.frame(ldply(1:10,.fun = function(x){c(runif(1),"a")}))

clr_all_results$num_cores <- as.data.frame(ldply(1:(nrow(clr_all_results)), .fun=findNumCores, type = "clr", completeRows = completeRowsClr))

#clr_all_results$num_cores <- lapply(1:(nrow(clr_all_results)), FUN=findNumCores, type = "clr", completeRows = completeRowsClr)
clr_all_results$num_cores <- ldply(1:(nrow(clr_all_results)), .fun=findNumCores, type = "clr", completeRows = completeRowsClr)

hifi_all_results$num_cores <- ldply(1:(nrow(hifi_all_results)), .fun = findNumCores, type = "hifi", completeRows = completeRowsHifi)

#hifi_all_results <- dplyr::rename(num_cores = V1)
#clr_all_results <- rename(num_cores = V1)

#hifi_all_results$num_cores <- lapply(1:(nrow(hifi_all_results)), FUN=findNumCores, type = "hifi", completeRows = completeRowsHifi)

```

```{r}
#extract total time (from submit to end)
findTotalTime <- function(rowNo, type, completeRows){
  path <- paste0("../pacbio_", type, "/phoenix_bench/submit_time.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
  data <- data[[1]][completeRows]
  submitTime <- str_extract(data[[rowNo]], '[:digit:]{4}-[:digit:]{2}-[:digit:]{2}T[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
  
  
path <- paste0("../pacbio_", type, "/phoenix_bench/end_time.txt")
  data <- read_file(path) %>% 
    strsplit('\n')
    data <- data[[1]][completeRows]
  endTime <- str_extract(data[[rowNo]], '[:digit:]{4}-[:digit:]{2}-[:digit:]{2}T[:digit:]{2}:[:digit:]{2}:[:digit:]{2}') 
  totalTime <- ymd_hms(endTime) - ymd_hms(submitTime)
  
  return(totalTime / dhours(1))
}

clr_all_results$total_time <- lapply(1:(nrow(clr_all_results)), FUN=findTotalTime, type = "clr", completeRows = completeRowsClr)

hifi_all_results$total_time <- lapply(1:(nrow(hifi_all_results)), FUN=findTotalTime, type = "hifi", completeRows = completeRowsHifi)

```

========================================================================================
#Processing Benchmarking snakemake files
========================================================================================

# Reading in benchmarking data

```{r}
clr_benchmark_files <- dir("../pacbio_clr/benchmarks", recursive=TRUE, full.names=TRUE, pattern=".tsv$")

clr_bench <- as_tibble(plyr::ldply(clr_benchmark_files, read.delim))

newCols <- c("rule_name",
             "threads",
             "read_type", 
             "assembly_type", 
             "assembly_tool", 
             "read_selection", 
             "prefix", 
             "bbduk_cov", 
             "bbduk_kmer", 
             "depth",
             "polishdepth",
             "polishselect",
             "polishround")

clr_bench[,newCols] <- NA

for( i in 1:length(clr_benchmark_files)) {
  temp <- unlist(strsplit(clr_benchmark_files[i], "/"))
  temp <- unlist(strsplit(temp, "_"))
  temp <- unlist(strsplit(temp, "\\."))
  clr_bench[i,"rule_name"] <- temp[match("benchmarks", temp) +1]
  clr_bench[i,"read_type"] <- "clr"
  clr_bench[i,"assembly_type"] <- temp[match("assemblytype", temp) +1]
  clr_bench[i,"assembly_tool"] <- temp[match("assemblytool", temp) +1]
  clr_bench[i,"read_selection"] <- temp[match("readselect", temp) +1]
  clr_bench[i,"prefix"] <- temp[match("prefix", temp) +1]
  clr_bench[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  clr_bench[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  clr_bench[i,"depth"] <- temp[match("depth", temp) +1]
  clr_bench[i,"polishdepth"] <- temp[match("polishdepth", temp) +1]
  clr_bench[i,"polishround"] <- temp[match("polishround", temp) +1]
  clr_bench[i,"polishselect"] <- temp[match("polishselect", temp) +1]
}

clr_bench$depth <- as.numeric(clr_bench$depth)

#change rule_name flyegenome to flye.
clr_bench$rule_name <- str_replace(clr_bench$rule_name, "flyegenome", "flye")

#====================================================================
#HIFI benchmarking Data
#====================================================================

hifi_benchmark_files <- dir("../pacbio_hifi/benchmarks", recursive=TRUE, full.names=TRUE, pattern=".tsv$")

hifi_bench <- as_tibble(plyr::ldply(hifi_benchmark_files, read.delim))

newCols <- c("rule_name",
             "threads",
             "read_type", 
             "assembly_type", 
             "assembly_tool", 
             "read_selection", 
             "prefix", 
             "bbduk_cov", 
             "bbduk_kmer", 
             "depth",             
             "polishdepth",
             "polishselect",
             "polishround")

hifi_bench[,newCols] <- NA

for( i in 1:length(hifi_benchmark_files)) {
  temp <- unlist(strsplit(hifi_benchmark_files[i], "/"))
  temp <- unlist(strsplit(temp, "_"))
  temp <- unlist(strsplit(temp, "\\."))
  hifi_bench[i,"rule_name"] <- temp[match("benchmarks", temp) +1]
  hifi_bench[i,"read_type"] <- "hifi"
  hifi_bench[i,"assembly_type"] <- temp[match("assemblytype", temp) +1]
  hifi_bench[i,"assembly_tool"] <- temp[match("assemblytool", temp) +1]
  hifi_bench[i,"read_selection"] <- temp[match("readselect", temp) +1]
  hifi_bench[i,"prefix"] <- temp[match("prefix", temp) +1]
  hifi_bench[i,"bbduk_cov"] <- temp[match("cov", temp) +1]
  hifi_bench[i,"bbduk_kmer"] <- temp[match("kmer", temp) +1]
  hifi_bench[i,"depth"] <- temp[match("depth", temp) +1]
  hifi_bench[i,"polishdepth"] <- temp[match("polishdepth", temp) +1]
  hifi_bench[i,"polishselect"] <- temp[match("polishselect", temp) +1]
  hifi_bench[i,"polishround"] <- temp[match("polishround", temp) +1]
}

hifi_bench$depth <- as.numeric(hifi_bench$depth)

#change rule_name flyegenome to flye.
hifi_bench$prefix <- str_replace(hifi_bench$prefix, "rice24kb", "24kb")
hifi_bench$prefix <- str_replace(hifi_bench$prefix, "SRR99694", "11kb")

```

# compare max rss for random genomes

```{r}
assemblers <- c("raven", "flye", "wtdbg2")
data1 <- subset(clr_bench, subset = rule_name %in% assemblers) 
data1 <- subset(data1, assembly_type == "genome") %>%
  subset(read_selection == "random") 

assemblers <- c("flye", "hifiasm")
data2 <- subset(hifi_bench, subset = rule_name %in% assemblers) 
data2 <- subset(data2, assembly_type == "genome") %>%
  subset(read_selection == "random")%>%
  subset(prefix == "24kb")

data3 <- subset(hifi_bench, subset = rule_name %in% assemblers) 
data3 <- subset(data3, assembly_type == "genome") %>%
  subset(read_selection == "random")%>%
  subset(prefix == "11kb")

ggplot(data1, aes(rule_name, max_rss, group = prefix, col=depth)) + 
  geom_point(size = 2, position = position_nudge(x=0)) + 
  xlab("Assembly Tool") +
  ylab("Max. Resident Set Size") +
  scale_y_continuous(labels = label_number(suffix = " Gb", scale = (1/1000))) +
  scale_colour_gradient("CLR\ncoverage",high = "#a54527", low = "#f4a187") +
  new_scale_color() +
  geom_point(data = data2, aes(color = depth), size = 2, position = position_nudge(x=-0.15)) +
  scale_colour_gradient("HiFi 24kb\ncoverage",high = "#463d58", low = "#d0ccd8") +
  new_scale_color() +
  geom_point(data = data3, aes(color = depth), size = 2, position = position_nudge(x=0.15)) +
  scale_colour_gradient("HiFi 11kb\ncoverage",high = "#388470", low = "#96d7c6") +
  theme(legend.position = "bottom",
        legend.text=element_text(size=7),
        legend.title = element_text(size=7),
        legend.key.width = unit(0.42,"cm"),
        legend.margin = margin(c(0.7,0.7,0.7,0.7))) +
  scale_fill_distiller() 

ggsave("images/allgenomes_max_rss.png",
         width = 5,
         height = 3,
         dpi = 300)

```

#Subset to get only assemblies completed on ronin.

```{r}
clr_bench$descriptor <- paste0(clr_bench$rule_name,
                               clr_bench$depth,
                               clr_bench$read_selection,
                               clr_bench$assembly_type)

hifi_bench$descriptor <- paste0(hifi_bench$rule_name,
                               hifi_bench$depth,
                               hifi_bench$read_selection,
                               hifi_bench$assembly_type)

clr_ronin <- c("flye10randomgenome",
               "flye25randomgenome",
               "raven50randomgenome",
               "wtdbg250randomgenome",
               "flye50randomgenome",
               "raven50longestgenome",
               "wtdbg250longestgenome",
               "flye50longestgenome",
               "raven75randomgenome",
               "wtdbg275randomgenome",
               "flye75randomgenome",
               "raven75longestgenome",
               "wtdbg275longestgenome",
               "flye75longestgenome",
               "raven100randomgenome",
               "wtdbg2100randomgenome",
               "flye100randomgenome",
               "raven100longestgenome",
               "wtdbg2100longestgenome",
               "flye100longestgenome",
               "raven125randomgenome",
               "wtdbg2125randomgenome",
               "flye125randomgenome",
               "raven125longestgenome",
               "wtdbg2125longestgenome",
               "flye125longestgenome",
               "raven150randomgenome",
               "wtdbg2150randomgenome",
               "flye150randomgenome",
               "raven150longestgenome",
               "wtdbg2150longestgenome")

hifi_11kbronin <- c("flye10randomgenome",
                "flye15randomgenome",
                "flye25randomgenome",
                "flye35randomgenome",
                "flye50randomgenome",
                "flye10longestgenome",
                "flye15longestgenome",
                "flye25longestgenome",
                "flye35longestgenome")
                
hifi_24kbronin <- c("hifiasm10randomgenome",
                "hifiasm15randomgenome",
                "hifiasm25randomgenome",
                "hifiasm35randomgenome",
                "hifiasm50randomgenome",
                "hifiasm60randomgenome",
                "hifiasm10longestgenome",
                "hifiasm15longestgenome",
                "hifiasm25longestgenome",
                "hifiasm35longestgenome",
                "hifiasm50longestgenome",
                "hifiasm60longestgenome",
                "flye10randomgenome",
                "flye15randomgenome",
                "flye25randomgenome",
                "flye35randomgenome",
                "flye50randomgenome",
                "flye60randomgenome",
                "flye10longestgenome",
                "flye15longestgenome",
                "flye25longestgenome",
                "flye35longestgenome",
                "flye50longestgenome",
                "flye60longestgenome")

clr_ronin_dat <- subset(clr_bench, descriptor %in% clr_ronin)

hifi_ronin24kb_dat <- subset(hifi_bench, prefix == "24kb") %>%
  subset(descriptor %in% hifi_24kbronin)

hifi_ronin11kb_dat <- subset(hifi_bench, prefix == "11kb") %>%
  subset(descriptor %in% hifi_11kbronin)

#join all three datasets together, add cores column = 48 and re-format to match benchmark data created from phoenix.

all_ronin_ass <- rbind(clr_ronin_dat, hifi_ronin24kb_dat, hifi_ronin11kb_dat)
all_ronin_ass$num_cores <- "48"

ronin_ass <- mutate(all_ronin_ass, core32 = s/as.numeric(num_cores)*32)

```


#CREATE RUNTIME GRAPH HERE!!!

```{r}
#3 datasets 

clr_results <- rbind(clr_canu_results, clr_all_results)
hifi_results <- rbind(hifi_canu_results, hifi_all_results)

clr_results <- clr_results %>% mutate(
  total_time_min = as.numeric(total_time) * 60)
hifi_results <- hifi_results %>% mutate(
  total_time_min = as.numeric(total_time) * 60)

clr_results <- clr_results %>% mutate(
  walltime_min = as.numeric(walltime) * 60)
hifi_results <- hifi_results %>% mutate(
  walltime_min = as.numeric(walltime) * 60)

clr_results$depth <- as.factor(as.numeric(clr_results$depth))
clr_results$read_selection <- factor(clr_results$read_selection)
hifi_results$depth <- as.factor(as.numeric(hifi_results$depth))
hifi_results$read_selection <- factor(hifi_results$read_selection)

#Filter clr and hifi results

tempclr <- subset(clr_results, assembly_type == "genome")
temphifi <- subset(hifi_results, assembly_type == "genome") 
tempclr <- subset(tempclr, rule_name %in% c("flye","wtdbg2","raven","canu","hicanu","hifiasm"))
temphifi <- subset(temphifi, rule_name %in% c("flye","wtdbg2","raven","canu","hicanu","hifiasm"))

ronin_cols <-   c("s", "num_cores","assembly_type","rule_name","read_selection","prefix","depth")
phoenix_cols <- c("walltime", "num_cores","assembly_type","rule_name","read_selection", "prefix",
                  "depth")
ronin_ass <- ronin_ass[,ronin_cols]
tempclr <- tempclr[,phoenix_cols]
temphifi <- temphifi[,phoenix_cols]

ronin_ass$s <- as.data.frame(ronin_ass$s/3600)
names(ronin_ass)[1] <- "walltime"

data <- bind_rows(ronin_ass, tempclr, temphifi)
data <- as.data.frame(rbind(ronin_ass, tempclr,temphifi))

temp <- mutate(data, cores32 = as.numeric(walltime)*(as.numeric(num_cores)/32))
```

```{r}
dat <- subset(data, prefix == "SRR99694")
dat$depth <- as.factor(dat$depth)
dat$rule_name <- as.factor(dat$rule_name)

ggplot(dat, aes(x = depth, y = walltime)) +
  geom_line()
```

missing11 <- ggplot(dat, aes(x=X2, y=X1, group=X5)) +
  geom_line(aes(color=X5)) +
  theme_bw() +
  xlab("Read Depth") + 
  colScale + 
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())+ 
  expand_limits(y=c(min_missing,max_missing))

```{r}
hifi <- hifi_all_results
hifi$num_cores <- as.numeric(hifi$num_cores)
hifi$walltime <- as.numeric(hifi$walltime)
hifi <- hifi %>% mutate(su = walltime * num_cores)

temp <- sum(subset(hifi,rule_name == "pbindex")$su)
temp <- temp + sum(subset(hifi,rule_name == "ccs")$su)
temp <- temp + sum(subset(hifi,rule_name == "pbmerge")$su)
temp <- temp + sum(subset(hifi,rule_name == "pbmerge_sample")$su)
temp <- temp + (14707/(60*60)*48)
Flye_hifi_11kb_50x_random_SU_hrs <- temp

clr <- clr_all_results
clr$num_cores <- as.numeric(clr$num_cores)
clr$walltime <- as.numeric(clr$walltime)
clr <- clr %>% mutate(su = walltime * num_cores)
subset(clr,rule_name == "flye")
Flye_clr_30kb_150x_random_SU_hrs <- 45334/(60*60)*48

#Flye 150x random clr genome on ronin = 45334 seconds at 48 cores
#Flye 50x srr99694 was done on ronin - 14707seconds and 48 cores


        #          bbduk           bbduk_genome             bbmap_sort 
        #              2                      1                      4 
        #      benchcanu                  busco                    ccs 
        #             50                     14                     40 
        #  contig_length                   flye generate_coverage_list 
        #             32                     24                      1 
        #         gfa2fa          gt_ltrharvest                hifiasm 
        #             40                     35                     43 
        # hifiasm_mummer          hifiasm_quast             ltr_finder 
        #             30                     15                     35 
        #  ltr_retriever                 mummer                pbindex 
        #             33                    120                      2 
        #        pbmerge         pbmerge_sample                  quast 
        #              2                      1                    106 
        #       quastref         select_longest                  seqtk 
        #            126                     27                     27 
```


Join together, format and add columns where necessary



Graph job time for rule_names

```{r}
data <- hifi_results %>% 
  filter(rule_name %in% c("flye", "wtdbg2","canu","hicanu")) %>%
  subset(assembly_type == "chloroplast") %>%
  subset(read_selection == "longest")

ggplot(data=data, aes(x = depth, y=as.numeric(walltime_min), fill=rule_name)) +
  geom_bar(stat="identity", position = "dodge") + 
  labs(x = "Assembly read depth") +
  labs(y = "Time in minutes") + 
  labs(rule_name = "Assembly tool") +
  labs(title = "Chloroplast assembly processing time")

ggplot(data=data, aes(x = depth, y=as.numeric(total_time_min), fill=rule_name)) +
  geom_bar(stat="identity", position = "dodge") + 
  labs(x = "Assembly read depth") +
  labs(y = "Time in minutes") + 
  labs(rule_name = "Assembly tool") +
  labs(title = "Chloroplast assembly submit to completion time")

ggplot(data=data, aes(x = depth, y=as.numeric(max_memory), fill=rule_name)) +
  geom_bar(stat="identity", position = "dodge") + 
  labs(x = "Assembly read depth") +
  labs(y = "Time in minutes") + 
  labs(rule_name = "Assembly tool") +
  labs(title = "Chloroplast assembly submit to completion time")

data <- clr_results %>% 
  filter(rule_name %in% c("flye", "raven","canu","wtdbg2")) %>%
  subset(assembly_type == "genome") %>%
  subset(read_selection == "longest")

ggplot(data=data, aes(x = depth, y=as.numeric(total_time), fill=rule_name)) +
  geom_bar(stat="identity", position = "dodge") + 
  labs(x = "Assembly read depth") +
  labs(y = "Time in hours") + 
  labs(rule_name = "Assembly tool") +
  labs(title = "Chloroplast assembly submit to completion time")

data <- hifi_results %>% 
  filter(rule_name %in% c( "hicanu","canu","hifiasm")) %>%
  subset(assembly_type == "chloroplast") %>%
  subset(read_selection == "random")

ggplot(data=data, aes(x = depth, y=as.numeric(max_memory), fill=rule_name)) +
  geom_bar(stat="identity", position = "dodge") + 
  labs(x = "Assembly read depth") +
  labs(y = "Max Memory in Mb") + 
  labs(rule_name = "Assembly tool") +
  labs(title = "Chloroplast assembly max memory usage") +
  scale_y_log10()

```




